SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-01-25 scipy-1.0/paper.tex
Reviewer feedback: add 1.0 and dev roadmap citations

From the user side, there were 13,096,468 downloads of SciPy from the Python
Packaging Index (PyPI) during the year 2017\cite{pypinfo}, which is a lower
bound on the number of total downloads by users given that downloading from
PyPI is only one of several popular methods to install SciPy.  The SciPy
website\cite{SciPylib}, which has been the default citation in the absence of a
peer-reviewed paper, has been cited $>3000$ times. Some of the most prominent
usages of or demonstrations of credibility for SciPy include the LIGO / Virgo
scientific collaboration that lead to the observation of gravitational waves
\cite{PhysRevLett.116.061102}, and the fact that SciPy is shipped directly with
MacOS and in the Intel Distribution for Python\cite{intel-python}.

@@

The SciPy Roadmap\cite{SciPy_roadmap} is a continuously-updated document
maintained by the community that describes some of the major directions for
improvement for the project, as well as specific limitations and matters that
require assistance moving forward.

@@

\texttt{fftpack} and {linalg} have too much functionality overlap with
\texttt{numpy} equivalents.

\texttt{scipy.interpolate} could benefit from a set of new features including
spline fitting routines with better user control; arithmetic routines for
splines; transparent tensor-product splines, Non-Uniform Rational B-Splines
support; and mesh refinement and coarsening of B-splines and corresponding
tensor products.  Some spline functionality in \texttt{scipy.signal} should be
migrated to \texttt{interpolate} and Second Order Sections need to be updated
to match the capabilities in other routines.

For \texttt{scipy.linalg}, the major change needed is to support a more recent
version of LAPACK. Users should be able access an increasing repertoire of
LAPACK functions using either \texttt{get\_lapack\_funcs} or
\texttt{sp.linalg.lapack.name\_of\_function}.

\texttt{scipy.optimize} would benefit from a few more good global optimizers 
as well as large-scale optimizers.

\texttt{scipy.ndimage} should be completely migrated to a data point
model (values on a grid), instead of a pixel model (elements with centers),
both of which have been used in the past, because the data point model is now
proving more effective in practice.

While \texttt{scipy.sparse} is mature, there are many data
formats and the community continues to move forward here so we will aim
to take advantage of their improvements\cite{abbasi2018sparse} 
while preserving backwards compatibility to the extent that it is possible.
\texttt{sparse.linalg} may benefit from wrappers for PROPACK 
for faster sparse SVD computation.

\texttt{scipy.spatial} will benefit from \texttt{spatial.transforms} with
support for rotation matrices.

\texttt{scipy.special} needs precision improvements for hypergeometric 
functions, parabolic cylinder functions, and spheroidal wave functions.

>>>>

From the user side, there were 13,096,468 downloads of SciPy from the Python
Packaging Index (PyPI) during the year 2017\cite{pypinfo}, which is a lower
bound on the number of total downloads by users given that downloading from
PyPI is only one of several popular methods to install SciPy.  The SciPy
website\cite{SciPylib}, which has been the default citation in the absence of a
peer-reviewed paper, has been cited $>3000$ times. Some of the most prominent
usages of or demonstrations of credibility for SciPy include the LIGO / Virgo
scientific collaboration that lead to the observation of gravitational waves
\cite{PhysRevLett.116.061102}, and the fact that SciPy is shipped directly with
MacOS and in the Intel Distribution for Python\cite{intel-python}. SciPy is used
by 47 \% of all machine learning projects on GitHub\cite{octoverse-scipy}.

@@

The SciPy Roadmap\cite{SciPy_roadmap_1,SciPy_roadmap_dev} is a
continuously-updated document
maintained by the community that describes some of the major directions for
improvement for the project, as well as specific limitations and matters that
require assistance moving forward.

@@

Some additional roadmap items are summarized in Table~\ref{table:roadmap}.

\begin{table}[H]
\caption{Summary of SciPy Roadmap items following 1.0 release}
\begin{tabular}{ c|c }
    SciPy submodule & Summary of Change \\
    \hline
    \texttt{optimize} & a few more high quality global optimizers\\
    \texttt{fftpack} & reduce overlap with NumPy equivalent \\
    \texttt{linalg} & reduce overlap with NumPy equivalent \\
    \texttt{interpolate} & new spline fitting and arithmetic routines \\
    \texttt{interpolate} & new transparent tensor-product splines\\
    \texttt{interpolate} & new Non-Uniform Rational B-Splines\\
    \texttt{interpolate} & mesh refinement \& coarsening of B-splines and tensor products\\
    \texttt{signal} & migrate spline functionality to \texttt{interpolate}\\
    \texttt{signal} & Second Order Sections update to match capabilities in other routines\\
    \texttt{linalg} & support a more recent version of LAPACK\\
    \texttt{ndimage} & migrate to data point model from pixel model\\
    \texttt{sparse} & incorporate sparse arrays from Sparse package\cite{abbasi2018sparse} \\
    \texttt{sparse.linalg} & add PROPACK wrappers for faster SVD\\
    \texttt{spatial} & add support for (quaternion) rotation matrices\\
    \texttt{special} & precision improvements for hypergeometric, parabolic cylinder, and spheroidal wave functions\\
\end{tabular}\label{table:roadmap}
\end{table}
